Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}

### 2018-01-28 Documents/M1/realizableFermionicM1/sections/realizability.tex
Proved Lemma 2.

\begin{lemma}
  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
\end{lemma}
\begin{proof}
  A convex set $Q$ is a set has the following property: 
  \begin{align}
  \theta a + (1-\theta)b \in Q, \text{\space} \text{for } \forall a, b \in Q \text{ and } 0\leq\,\theta\,\leq1. 
  \end{align} 
  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
  Let's prove it is true.

  For the first component
  \begin{align}
  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b},
  \end{align}
  since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative ($\cJ_{ab}\geq0$).
  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, 
  \begin{align}
  \cJ_{ab} \leq \theta \cdot 1 + (1-\theta) \cdot 1 = 1.
  \end{align}
  Therefore, $\cJ_{ab} \in [0,1]$.

  For the second component,
  \begin{align}
  \vect{\cH}_{ab} 
  & = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b} \nonumber\\
  & = \f{1}{4\pi}\int_{\bbS^{2}} \left[ \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \right] \bl(\omegaNu) d\omegaNu. 
  \end{align}
  Since $\theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu) \in [0,1]$, we can define $\tilde{f} = \theta\,f_{a}(\omegaNu) + (1-\theta) f_{b}(\omegaNu)$.
  $\tilde{f} \ in [0,1]$ and 
  \begin{align}
  \cJ_{ab} = \f{1}{4\pi}\int_{\bbS^{2}} \tilde{f} d\omegaNu \\
  \vect{\cH}_{ab} = 
  \end{align}
\end{proof}

>>>>

\begin{lemma}
  The set $\cR$, defined in Eq.~\eqref{eq:realizableSet}, is convex.  
\end{lemma}
\begin{proof}
  A convex set $Q$ is a set has the following property: 
  \begin{equation*}
  \theta a + (1-\theta)b \in Q,~\text{for}~\forall a, b \in Q~\text{and}~0\leq\,\theta\,\leq1. 
  \end{equation*} 
  Let $\vect{\cM}_{a}=\big(\cJ_{a},\vect{\cH}_{a}\big)^{T}$ and $\vect{\cM}_{b}=\big(\cJ_{b},\vect{\cH}_{b}\big)^{T}$ to be two arbitrary elements of $\cR$.
  If $\cR$ is convex, we will have $\vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} = \theta \vect{\cM}_{a} + (1-\theta)\vect{\cM}_{b}$ in $\cR$ with $0\leq\theta\leq1$.
  The first component of $\vect{\cM}_{ab}$ is
  \begin{equation*}
  \cJ_{ab} = \theta \cJ_{a} + (1-\theta)\cJ_{b}.
  \end{equation*}
  Since $\theta$, $\cJ_{a}$, $1-\theta$ and $\cJ_{b}$ are all nonnegative, $\cJ_{ab}$ is also nonnegative.
  Meanwhile, since $\cJ_{a}\leq1$ and $\cJ_{b}\leq1$, $\cJ_{ab}\leq1$.
  That's $\cJ_{ab} \in [0,1]$.
  The second component is
  \begin{equation*}
  \vect{\cH}_{ab} 
  = \theta \vect{\cH}_{a} + (1-\theta)\vect{\cH}_{b}.
  \end{equation*}
  Using Jensen's inequality,
  \begin{equation*}
  \gamma(\vect{\cM_{ab}}) \leq \theta\gamma(\vect{\cM_{a}}) + (1-\theta)\gamma(\vect{\cM_{b}}) \leq 0.
  \end{equation*}
\end{proof}
